Qualitative Assessesment of Graph Neural Network Potentials for Phonon Properties of Shape Memory Alloys using Graph Neural Network Potentials

### 2024-01-09 src/tex/ms.tex
Add info and reworking plotting.

\begin{figure}[ht!]
    \script{PlotCohesiveEnergy.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/NiTi_CohesiveEnergyPlot.png}
        \caption{
          Comparison of predicted cohesive energy for respective ground-state structure and model. As a reference we use The Materials Project entry for the \ce{NiTi} \textit{B2} entry \cite{MP--571}.
        }
        \label{fig:ecoh}
    \end{centering}
\end{figure}

>>>>

\begin{figure}[ht!]
    \script{PlotCohesiveEnergy.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/NiTi_CohesiveEnergyPlot.png}
        \caption{
          Comparison of predicted \ce{NiTi} cohesive energy for respective ground-state structure and model. As a reference we use The Materials Project entry for the \ce{NiTi} \textit{B2} entry \cite{MP--571}.
        }
        \label{fig:ecoh_niti}
    \end{centering}
\end{figure}

\begin{figure}[ht!]
    \script{PlotCohesiveEnergy.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/PtTi_CohesiveEnergyPlot.png}
        \caption{
          Comparison of predicted \ce{PtTi} cohesive energy for respective ground-state structure and model.
        }
        \label{fig:ecoh_ptti}
    \end{centering}
\end{figure}
